Architectures and Open pNets

### 2018-03-26 2018-Arch-pNets/arch-pNets.tex
Now compiles :)
WEAK: removed a TODO and added a TODO section at the begining
Clean up the notation paragraph

We extensively use \replaceSB{indexed structures
over some countable indexed sets, which are equivalent to mappings over
the countable set. }{structures indexed over some finite or countable sets of indices, which can be equivalently defined as mappings over such index sets. }% . The indexes will usually be
% integers, bounded or not. Such an indexed family is
%denoted
%follows:
\addSB{Thus, }
$a_i^{i\in I}$
%, or equivalently  $(i\mapsto a_i)^{i\in I}$
denotes a family of elements $a_i$ indexed over the
set $I$. % Such a family
% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
% To specify the set over which the structure is indexed,
% indexed structures are always denoted with an exponent of the form $i\in I$
% (arithmetic only appears in the indexes if necessary).
\replaceSB{$a_i^{i\in I}$ }{This notation }defines both $I$ the set over which the family is
indexed (called \emph{range}), and $a_i$ the elements of the family.
E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
$3$ ; abbreviated $(3\mapsto a)$ in the following.
When this is not
ambiguous, we shall use notations for sets, and typically write
``indexed set over I''\replaceSB{ when}{, even though} formally we should speak of multisets; and
write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
family is denoted $\emptyset$. \replaceSB{
We denote classically with an overline -- $\overline{a}$ -- a family when the indexing set 
is
not meaningful.}{We use a classical overline notation, \eg $\overline{a}$, for a family, where the indexing set is irrelevant} \replaceSB{$\uplus$ is }{Finally, we use $\uplus$ to denote }the disjoint union on
indexed sets.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\\noteSB{I would not put a new line here}
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] \noteSB{This is clear from $\pNet_i^{i\in I}$.}\hl{$I \in \I$ is the set over which sub-pNets are indexed.}
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
%sub-pNets are indexed.

@@

\item
The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
itself plus the indexes of all the holes of its subnets (we suppose those indexes 
disjoints).
%
%defined inductively; the sets of holes
%in a pNet node and its subnets are all disjoint:
%  \[\begin{array}{l}
%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
%=J\uplus{\displaystyle \bigcup_{i\in 
%I}\Holes(\pNet_i)}\\
%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
%\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
is said to be \emph{open}.

\subsection{Operational Semantics for Open pNets}
\label{section:op-semantics}

>>>>

We extensively use indexed structures
over some countable indexed sets, which are equivalent to mappings over
the countable set. 
Thus, 
$a_i^{i\in I}$
%, or equivalently  $(i\mapsto a_i)^{i\in I}$
denotes a family of elements $a_i$ indexed over the
set $I$. % Such a family
% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
% To specify the set over which the structure is indexed,
% indexed structures are always denoted with an exponent of the form $i\in I$
% (arithmetic only appears in the indexes if necessary).
This notation defines both $I$ the set over which the family is
indexed (called \emph{range}), and $a_i$ the elements of the family.
E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
$3$ ; abbreviated $(3\mapsto a)$ in the following.
When this is not
ambiguous, we shall use notations for sets, and typically write
``indexed set over I'', even though formally we should speak of multisets; and
write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
family is denoted $\emptyset$. We use a classical overline notation, \eg $\overline{a}$, 
for a family, where the indexing set is irrelevant. Finally, we use $\uplus$ to denote 
the disjoint union on
indexed sets.

@@

\todoLH{Guard syntax???}
\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\\noteSB{I would not put a new line here}
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] \noteSB{This is clear from $\pNet_i^{i\in I}$.}\hl{$I \in \I$ is the set over which sub-pNets are indexed.}
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
%sub-pNets are indexed.

@@

\item
The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
itself plus the indexes of all the holes of its subnets (we suppose those indexes 
disjoints).
%
%defined inductively; the sets of holes
%in a pNet node and its subnets are all disjoint:
%  \[\begin{array}{l}
%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
%=J\uplus{\displaystyle \bigcup_{i\in 
%I}\Holes(\pNet_i)}\\
%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
%\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
is said to be \emph{open}.
\end{itemize}
\end{definition}
\subsection{Operational Semantics for Open pNets}
\label{section:op-semantics}
